---
title: "The Cauchy Distribution"
subtitle: "Weird But Fascinating"
output:
 xaringan::moon_reader:
   lib_dir: libs
   nature:
     highlightStyle: github
     highlightLines: true
     countIncrementalSlides: false
---
 
```{r, echo = F, message = F, warning = F, fig.align='center'}
library(tidyverse)
knitr::opts_chunk$set(fig.width = 10, fig.height = 7, fig.align = 'center')
```
 
# Facts About the Cauchy Distribution

* The Cauchy distribution does not have any moments

--

* $X,Y \sim N(0,1) \Rightarrow \frac{X}{Y} \sim Cauchy(0,1)$  

--

* The Cauchy distribution is a special case of the Student-t disbtribution 

--

* The Cauchy distribution is stable, that is a linear combination of Cauchy
  random variables has Cauchy distrbution

--

---

# A Histogram of 1000 Cauchy(0,1) Realizations
 
```{r, echo=F}
set.seed(2702)
nof_samples = 1000
cauchy_sample = rcauchy(1000)
cauchy_tib = tibble(cauchy = cauchy_sample)

ggplot(cauchy_tib) +
    geom_histogram(aes(x = cauchy), binwidth = 1)
```
 
---

# Extreme Values in Our Sample

```{r, highlight.output=c(1, 5)}
cauchy_tib %>%
    top_n(5, wt = abs(cauchy))
```

---
